---
title: "datavyur"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{datavyur}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(datavyur)
```

## About

Datavyu (<https://datavyu.org>) is a free, open-source, desktop tool for annotating video files.

Datavyu files have an extension of `.opf`, but under-the-hood, Datavyu files are ASCII text in a zip-file wrapper.
This makes them easy to decode and manipulate outside of the application.

Datavyu is closely associated with Databrary (<https://databrary.org>), a web-based data library specialized for storing and sharing research video.
But Datavyu can and is regularly used by researchers who do not use Databrary.

## Getting started

You do not need to download and install the Datavyu desktop application to use the `datavyuR` package.
But this vignette uses the `databraryr` package to download a publicly shared Datavyu file and its accompanying video.
The `databraryr` package is currently available on GitHub (<https://github.com/databrary/datavyuR>).
If you do not have it installed, install `devtools` with `install.packages('devtools)`, and then install `databraryr` with `devtools::install_github('databraryr')`.

Once that is done, we can download a sample Datavyu spreadsheet from <https://databrary/volume/1>.

<!-- TODO(ROG/JS): How to use temporary directories and file names? -->

```{r, eval=FALSE}
datavyur::download_opf()
```

The `datavyur::download_opf()` command creates a long name for this file.
The reason is that Datavyu files do not (yet) contain (much) robust information about which video or audio file they are linked to.
Nor do Datavyu files contain information about where the files came from on Databrary.
So, the file name contains the Databrary-unique volume ID, the session (folder) ID, and the asset (file) ID, plus a date/time stamp to make each download unique.
None of this Databrary-specific metadata matters to us if we won't be using the `datavyuR` package to interact with files that aren't stored on Databrary.

To get meaningful information out of the Datavyu file, we need to extract it into its three component parts.

```{r, eval=FALSE}
extract_dv("tmp")
```

We see that there are three new files with names `1`, `db`, and `project`.

`1` contains information about the video file associated with the Datavyu file.
`project` contains metadata about the Datavyu coding sheet and where the original video file used to generate the coding spreadsheet came from.
`db` contains the actual time-locked codes.

